Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-12 article/article.tex
review
nonono

Table~\ref{tab:results} illustrates the overall performance of the three classifiers. Rows indicate various feature selection methods. We applied PCA to the original data, while for the rest feature selection methods were applied to the data belonging to the selected ROIs (cf.~Section~\ref{sec:dimensionalityReduction}). For instance, \emph{Norm/Vox-M ROIs} indicates that we normalized over the voxel values of the same voxel index using the mean and standard deviation, while \emph{Norm-M-SD ROIs} indicates that we normalized over the voxel values of the same scan index using the mean and standard deviation. Columns depict the used classifiers. For the classifiers depicted with *, we used a different method for structuring the data, as described in Section~\ref{sec:trainingMethodsAndClassifiers}.

>>>>

Table~\ref{tab:results} illustrates the overall performance of the three classifiers. Rows indicate various feature selection methods. We applied PCA to the original data, while for the rest feature selection methods were applied to the data belonging to the selected ROIs (cf.~Section~\ref{sec:dimensionalityReduction}). For instance, \emph{Norm/Vox-M ROIs} indicates that we normalized over the voxel values of the same voxel index using the mean and standard deviation, while \emph{Norm-M-SD ROIs} indicates that we normalized over the voxel values of the same scan index using the mean and standard deviation. Columns depict the used classifiers. For the classifiers depicted with *, we used the method of estimating the parameters per scan, as described in Section~\ref{sec:trainingMethodsAndClassifiers}.
